**Department Invited Speakers Do Not Reflect Trainee Diversity**

### 2019-09-05 submission/manuscript.Rmd
further outline manuscript, add Diversify

@@

**Code and data availability.** The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/.

@@

500 words. In this study

+ there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
+ perspective is often as/more important than self-identification -- in addition to self-selecting on Diversify lists, consider sharing more about their past
+ idea for departments to invite speakers to share about their personal story as well as their science
+ use Diversify sources
+ US-serving institutions, need to pay attention to US-HURM

@@

@@

>>>>

+ previous examinations have focused on conferences and panels, large number of people in a short period of time -- easy to make comparisons & see trends

+ more difficult to see trends over long time period -- asked cumulative trends of speakers over 5 year period, "normative" to trainees in the department

@@

**Code and data availability.** The anonymized data, code for all analysis steps, and an Rmarkdown version of this manuscript is available at https://github.com/akhagan/Hagan_Libertucci_SpeakerDiversity_XXXX_2019/. Template and complete instructions for generating a field-specific Diversity website are available at https://github.com/diversifymicrobiology/DiversifyMicrobiology.github.io/.

@@

+ Gender
    + decreasing representation of women in each role (as prestige increases)
    + compare to global stats of Micro resources 60:40 (Elseiver)
    + previous study at 50 US universities focusing on genders
    + discuss factors that decrease speaking invitations to women

+ Under represented minorites
    + overrepresentation of Caucasian individuals as Faculty & Speakers, relative to trainees
    + decline in HURM & International as Fac/Speak, relative to trainees
    + inclination to lump HURM & International together to improve diversity stats
    + important to distinguish separately as both face different issues in the US & academy

+ Improving speaker diversity
    + US-serving institutions have particular responsibility to those historically supressed populations
    + to improve retention of white women & HURMs, each group needs equivalent representation to counteract biases and improve self-efficacy
    + recall bias not the only issue, also not always possible to identify members of historically underserved communities
    + example: there are speakers who have URM status, but it wasn't readily apparent from the internet/CV 
    + perspective is often as/more important than self-identification

+ Development of Diversify tools
    + inspired by EEB/Chemistry
    + tool for members of URM groups to self-identify & for others to use to find diverse candidates
    + describe maintanence of lists (Rebecca)
    + describe website creation

+ Other resources/ideas
    + student/lab invited speakers -- improve diversity of suggestions (fields/careers)
    + departments to invite speakers to share about their personal story as well as their science

@@

+ increased retention of white women & HURMS -- increasing representation of 
+ tools available to create field specific lists of H underserved

@@

## Author Contributions
A.K.H. collected the data, assigned demographics, analyzed the data, and created the website. R.P. created the lists, forms, and website content. J.L. wrote the introduction and provided conceptual advice. All authors contributed to the final manuscript.

Table 1. List of Suggestions & Resources
